Gelation as a condensation frustrated by hydrodynamics and mechanical tension

### 2015-08-10 gel_cond/trunk/paper.tex
Fix Debye lengths with and without salt

In the absence of salt, the Debye length is expected to reach \SI{100}{\nano\metre} and the (weakly) charged colloids experience a long range electrostatic repulsion. We confirm that colloids never come close enough to feel the short-ranged attraction. Screening by tetrabutylammonium bromide (Fluka) at saturated concentration brings down the Debye length to about \SI{13}{\nano\metre}, practically discarding the repulsion.

>>>>

In the absence of salt, the Debye length is expected to reach several \si{\micro\metre} and the (weakly) charged colloids experience a long range electrostatic repulsion. We confirm that colloids never come close enough to feel the short-ranged attraction. Screening by tetrabutylammonium bromide (Fluka) at saturated concentration brings down the Debye length to about \SI{100}{\nano\metre}, practically discarding the repulsion.
